---
title: "R Assignment 2"
output:
  pdf_document: default
  word_document: default
date: '2022-04-08'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Data
```{r}
Data <- read.csv("C:/Users/prana/Downloads/archive (1)/Kaagle_Upload.csv", header=FALSE)
```
#Print Structure
```{r}
str(Data)
```
#List Variables
```{r}
ls(Data)
```
#Print the top 15 rows
```{r}
head(Data, 15)
```
#User defined function and new data frame
```{r}
MEAN <- function (x){
result <- mean(x)
print(result)
}
mydata <- data.frame(vehicle.m = c(18, 9, 4, 15, 9, 4, 14, 4, 18, 4, 14, 5, 18, 2 ,2), driver.age = c(45, 25, 51, 50, 27, 46, 27, 33, 24, 25, 43, 29, 43, 41, 23), vehicle.age = c(11, 1, -1, 1, -1, -1, 8, 10, 1, 8, 6, -1, 5, 1, 1))
MEAN(mydata$driver.age)
```
#Filter rows
```{r}
print(filter(Data, "V16"=="45" & "V20"=="11"))
```
#Remove missing values
```{r}
library(dplyr) 
Data %>% distinct("V1", .keep_all= TRUE)
```
#Rename some of column names
```{r}
colnames(Data)[colnames(Data) %in% c("V2", "V3", "V4") ] <- c("V.ref", "V.type", "t&a")
```
#Add new variables by using a mathematical function
```{r}
mydata %>% mutate(Newage = driver.age*2)
```
#Create a training set
```{r}
RandomNum <- runif(50, 1, 99)
```
#Print the summary Statistics
```{r}
summary(Data)
```
#Perform statistical functions
```{r}
mean(mydata$driver.age)
median(mydata$driver.age)
mode(mydata$driver.age)
range(mydata$driver.age)
```
#Plot a scatter plot
```{r}
plot(mydata$driver.age, mydata$vehicle.age, main = "Driver age Vs Vehicle age", xlab = "Age of driver", ylab = "Age of Vehicle")
```
#plot bar plot
```{r}
library(ggplot2)
ggplot(data = Data, aes( x="v16", fill= factor("v35")))+ geom_bar()
```
#correlation between two variables by applying least square linear regression model
```{r}
cor(mydata$driver.age, mydata$vehicle.age)
```
```{r}
```
